A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-09-29 paper/paper.tex

The left TPJ in turn exhibits a close topographical relationship to
Wernicke's area
involved in the comprehension or understanding of written and spoken language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integrating of world knowlege.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing any language content
(Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Also inner speech hinges on knowledge retrieval of statistical structure
about the physical and inter-personal world.
Multivariate volumetric analyses showed that the internal production of
formulated thought ("language of the mind") is closely related to the left TPJ
(Geva et al., 2011).
A number of neuroimaging studies demonstrated LTPJ activity responses
to sementically aberrant words in sentences, which suggests a role
in binding a given semantic concept into an integrated whole.
Further,
episodic memory recall and imagination strongly draws on
complex world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forcast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived models of the world
into ongoing action, planning, and problem solving.
world -> policy matrix driven computation
self -> value matrix driven computation

@@

\section{Relation to Other Statistical Models (Elvis)}
\paragraph{Control Theory.}
abc

>>>>

The left TPJ in turn exhibits a close topographical relationship to
Wernicke's area
involved in the comprehension or understanding of written and spoken language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integrating of world knowlege.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing any language content
(Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Also inner speech hinges on knowledge retrieval of statistical structure
about the physical and inter-personal world.
Multivariate volumetric analyses showed that the internal production of
formulated thought ("language of the mind") is closely related to the left TPJ
(Geva et al., 2011).
A number of neuroimaging studies demonstrated LTPJ activity responses
to sementically aberrant words in sentences, which suggests a role
in binding a given semantic concept into an integrated whole.
Further,
episodic memory recall and imagination strongly draw on
complex world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forcast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived models of the world
into ongoing action, planning, and problem solving.
world -> policy matrix driven computation
self -> value matrix driven computation

@@

\section{Relation to other statistical models (Elvis)}
\paragraph{Control theory.}
\begin{itemize}
  \item The model proposed in \cite{betzel2016} can be cast in the form \eqref{eq:hj}, with the particular choice $\Q = \textbf{I} = \rho^{-1}\R$ and $\Q_{\text{fin}} = \textbf{0}$, but with a rather ad-hoc handle on stability issues and choice driver nodes...
\end{itemize}
